A fault tolerant multi-server system for MMOGs

### 2011-07-07 textos/phd-prospectus/prospectus.tex
consistency figure

Figure \ref{fig:consistency} illustrates two avatars, each situated in a different region -- managed, therefore, by different server groups --, but still close enough to interact. Each command issued by their players has to be forwarded to the groups that manage some object in its target set. This is done by multicast.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Optimistic multicast} \label{sec:optmcast}

@@

We devised, then, a multicast protocol that, although not genuine, allows the system to increase its scale without getting flooded with control messages. We call it \emph{quasi-genuine}, because every group keeps sending messages to (and receiving from) other groups, even if there is no application level message to be exchanged, but only the ones with which it can exchange messages. The information concerning which other groups a given group can communicate with is given by the application.

This can be used by our consistency management algorithm because every server group only has to forward commands to a specific set of groups, which are the ones managing neighbor regions, and this is known as soon as the partitioning has been performed. If the partioning changes, the set of group pairs which can communicate with each other is also reconfigured.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future work} \label{sec:futurework}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activities and publications} \label{sec:achievements}
%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Figure \ref{fig:consistency} illustrates two avatars situated in regions managed by different server groups, but still close enough to interact. Each command issued by their players has to be forwarded to the groups that manage some object in its target set, which is done by multicast.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.8\linewidth]{images/consistency}
  \caption{Multicasting a command to a group which manages an object in that command's target set}
  \label{fig:consistency}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-genuine multicast} \label{sec:optmcast}

@@

We devised, then, a multicast protocol that, although not genuine, allows the system to increase its scale without getting flooded with control messages. We call it \emph{quasi-genuine}, because every group keeps sending messages to (and receiving from) other groups, even if there is no application level message to be exchanged, but only the ones with which it \emph{is possible to} exchange messages. The information concerning which other groups a given group can communicate with is given by the application.

The advantage of a quasi-genuine multicast protocol is that it would be a middle ground between genuine and non-genuine protocols, inheriting some advantages from both -- namely, improved scalability and lower message delivery time --, at the cost of restricting which groups can communicate with each other. Although the system can be reconfigured to change the group pairs that are able to exchange messages, such reconfiguration will have some cost, so this multicast protocol is more suitable for applications where this would not be frequent.

This can be used by our consistency management algorithm because every server group only has to forward commands to a specific set of other groups, which are the ones managing neighbor regions, and this is known as soon as the partitioning has been performed. Changes to the partioning should be performed rarely, as it would incur in some players migrating between servers. Therefore, the set of group pairs that can communicate with each other will not change frequently.

To further decrease the message delivery time, an optimistic delivery will also be employed. By assigning timestamps based on the local clocks -- which are supposed to be more or less synchronized -- and by every server waiting long enough for messages to arrive from another servers before performing the delivery, the final total message order will most likely match the timestamp order, so that the messages could be delivered in only one communication step, although that delivery would have to be confirmed by some conservative delivery.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future work} \label{sec:futurework}

We are currently workings towards the validation of both the optimistic multicast

%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Activities and publications} \label{sec:achievements}

Some related work that we have published so far include:
%%%%%%%%%%%%%%%%%%%%%%%%%
